Thermodynamic response functions in a cell fluid model

### 2024-09-13 paper_text.tex
update paragraph on applicability

Note that the theoretical approach used here has certain limits of applicability. The point is that the equations of state \eqref{eq:eosMT} and \eqref{eq:eosNT} of the cell fluid model are derived from calculating the grand partition function in the zero mode approximation of the $\rho^4$-model. At one stage of the calculation, we establish an explicit connection between the effective chemical potential $\bar M$ and the density $\rho^*$ by solving the cubic equation, which is derived from combining equations~\eqref{eq:density} and~\eqref{eq:ro_M} (see \cite{KozlovskiiDobush2020}, Section 5). This equation has three roots. Two solutions are nonphysical because they consequently reflect a decrease in chemical potential with increasing density. The third solution, namely \eqref{eq:ro_nT}, indicates the growth of the chemical potential with increasing density, but it is only valid for a limited range of densities $\rho^*_{min} \leqslant \rho^* \leqslant \rho^*_{max}$, where 
	\begin{eqnarray}
		\rho^*_{min} &=& \rho^*_c - \left( \frac{\left( g_3^2 - 2 g_2 g_4\right)^3}{9 g_4^4}\right)^{\frac{1}{2}}, \\
		\rho^*_{max} &=& \rho^*_c + \left( \frac{\left( g_3^2 - 2 g_2 g_4\right)^3}{9 g_4^4}\right)^{\frac{1}{2}}. \nonumber
	\end{eqnarray}
	The density's marginal values vary depending on the selected parameters $\alpha^*$ and $p$. Providing the set of coefficients \eqref{params}, one has $\rho^*_{min} = 0.009$ and $\rho^*_{max} = 1.946$.

>>>>

The equations of state~\eqref{eq:eosMT} and \eqref{eq:eosNT} are derived in the zero-mode approximation of the $\rho^4$-model, which imposes limits on their applicability. Specifically, in terms of density, the equations are  applicable for $\rho^*_{\rm min} \leq \rho^* < \rho^*_{\rm max}$, where $\rho^*_{\rm min}$ and $\rho^*_{\rm max}$ are determined by the parameters $\alpha^*$ and $p$. For parameters given in~\eqref{params}, these values were estimated in~\cite{KozlovskiiDobush2020} as $\rho^*_{\rm min} = 0.009$ and $\rho^*_{\rm max} = 1.946$.
